Quantum Interval-Valued Probability: Contextuality and the Born Rule

### 2017-10-01 prop_letter.tex
prop_letter.tex \section{Gleason} Updating...

\noindent To prove the theorem, we first need to construct a QIVPM,
and then verify that no states consistent with it on all projectors.
Given an orthonormal basis $\left\{ \ket{0},\ket{1},\ket{2}\right\} $,
let $\mathscr{I}_{0}=\left\{ \necess,\imposs,\unknown\right\} $,
$\ket{\ps}=\left(\ket{0}+\ket{1}\right)/\sqrt{2}$, and $\ket{\ps'}=\left(\ket{0}+\ket{2}\right)/\sqrt{2}$.
The function~$\bar{\mu}:\events\rightarrow\mathscr{I}_{0}$ defined
in Table~\ref{tab:non-Born-QIVPM} can be verified as a QIVPM straightforwardly.
\begin{table}
\caption{\label{tab:non-Born-QIVPM}Define a QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}_{0}$
on the three-dimensional Hilbert space. The projectors mapping to
the same interval is listed in the column labeled by $P$ and separated
by commas.}

@@

In other words, if the measurement intervals are too imprecise, the
results we get might contradict to each other, and exclude all possible
states consistent with the measurement results. To avoid this problem,
instead of proposing an abstract framework~\citep{HOSTunpublished},
we start from a concrete family of intervals as follow:
\begin{equation}
\begin{aligned}\mathscr{I}_{n}= & \set{\left[\tfrac{k-1}{2n},\tfrac{k+1}{2n}\right]\cap\left[0,1\right]}{k=0,\ldots,2n}\\
 & \cup\{\imposs,\necess\}
\end{aligned}
\end{equation}
which are overlapping intervals with length~$1/n$ except for the
intervals with length~$\left(2n\right)^{-1}$ at each end. As shown
in Table~\ref{tab:I_n}, for each interval~$[\ell,r]$, we define
$\textrm{Int}\left([\ell,r]\right)$, the non-overlapping interior
part of $[\ell,r]$.
\begin{table}
\caption{\label{tab:I_n}Intervals in $\mathscr{I}_{n}$, their lengths, and
their interiors, where $2\mid k$ means $k$ is even, and $2\nmid k$
means $k$ is odd. Although intervals~$[\ell,r]$ are overlapping,
their interior~$\textrm{Int}\left([\ell,r]\right)$ are non-overlapping.}

\begin{tabular}{cccc}
\toprule 
\addlinespace
$k$ & $[\ell,r]$ & $r-\ell$ & $\textrm{Int}\left([\ell,r]\right)$\tabularnewline\addlinespace
\midrule
\midrule 
\addlinespace
 & $\imposs$ & $0$ & $\imposs$\tabularnewline\addlinespace
\midrule 
\addlinespace
$0$ & $\left[0,\tfrac{1}{2n}\right]$ & $\tfrac{1}{2n}$ & $\left(0,\tfrac{0.5}{2n}\right]$\tabularnewline\addlinespace
\midrule 
\addlinespace
\begin{tabular}{c}
$0<k<2n$\tabularnewline
and $2\nmid k$\tabularnewline
\end{tabular} & $\left[\tfrac{k-1}{2n},\tfrac{k+1}{2n}\right]$ & $\tfrac{1}{n}$ & $\left(\tfrac{k-0.5}{2n},\tfrac{k+0.5}{2n}\right)$\tabularnewline\addlinespace
\midrule 
\addlinespace
\begin{tabular}{c}
$0<k<2n$\tabularnewline
and $2\mid k$\tabularnewline
\end{tabular} & \multirow{1}{*}{$\left[\tfrac{k-1}{2n},\tfrac{k+1}{2n}\right]$} & $\tfrac{1}{n}$ & $\left[\tfrac{k-0.5}{2n},\tfrac{k+0.5}{2n}\right]$\tabularnewline\addlinespace
\midrule 
\addlinespace
$2n$ & $\left[\tfrac{2n-1}{2n},1\right]$ & $\tfrac{1}{2n}$ & $\left[\tfrac{2n-0.5}{2n},1\right)$\tabularnewline\addlinespace
\midrule 
\addlinespace
 & $\necess$ & $0$ & $\necess$\tabularnewline\addlinespace
\bottomrule
\end{tabular}
\end{table}
Since the interior part of intervals are non-overlapping, we can define
a function~$\iota_{n}:\left[0,1\right]\rightarrow\mathscr{I}_{n}$
by selecting the interval~$\iota_{n}\left(x\right)=[\ell,r]$ if
$x\in\textrm{Int}\left([\ell,r]\right)$.

>>>>

\noindent To prove the theorem, we first need to construct a QIVPM,
and then verify that no states consistent with it on all projectors.
Given an orthonormal basis $\left\{ \ket{0},\ket{1},\ket{2}\right\} $,
let $\mathscr{I}_{0}=\left\{ \necess,\imposs,\unknown\right\} $,
$\ket{\ps}=\left(\ket{0}+\ket{1}\right)/\sqrt{2}$, and $\ket{\ps'}=\left(\ket{0}+\ket{2}\right)/\sqrt{2}$.
The function~$\bar{\mu}:\events\rightarrow\mathscr{I}_{0}$ defined
in Table~\ref{tab:non-Born-QIVPM} can be verified as a QIVPM straightforwardly.
\begin{table}
\caption{\label{tab:non-Born-QIVPM}Define a QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}_{0}$
on the three-dimensional Hilbert space. The projectors mapping to
the same interval are listed in the column labeled by $P$ and separated
by commas.}

@@

In other words, if the measurement intervals are too imprecise, the
results we get might contradict to each other, and exclude all possible
states consistent with the measurement results. Although we will not
dig into the general abstract framework to avoid this problem here~\citep{HOSTunpublished},
we will solve this problem with a concrete family of intervals and
QIVPMs. The following intervals 
\begin{equation}
\begin{aligned}\mathscr{I}_{n}= & \set{\left[\tfrac{k-1}{2n},\tfrac{k+1}{2n}\right]\cap\left[0,1\right]}{k=0,\ldots,2n}\\
 & \cup\{\imposs,\necess\}
\end{aligned}
\end{equation}
are overlapping intervals with length~$1/n$ except for the intervals
with length~$\left(2n\right)^{-1}$ at each end. As shown in Table~\ref{tab:I_n},
for each interval~$[\ell,r]$, we define $\textrm{Int}\left([\ell,r]\right)$,
the non-overlapping interior part of $[\ell,r]$.
\begin{table}
\caption{\label{tab:I_n}Intervals in $\mathscr{I}_{n}$, their lengths, and
their interiors, where $2\mid k$ means $k$ is even, and $2\nmid k$
means $k$ is odd. Although intervals~$[\ell,r]$ are overlapping,
their interior~$\textrm{Int}\left([\ell,r]\right)$ are non-overlapping.}

\begin{tabular}{cccc}
\toprule 
\addlinespace
$k$ & $[\ell,r]$ & $r-\ell$ & $\textrm{Int}\left([\ell,r]\right)$\tabularnewline\addlinespace
\midrule
\midrule 
\addlinespace
 & $\imposs$ & $0$ & $\imposs$\tabularnewline\addlinespace
\midrule 
\addlinespace
$0$ & $\left[0,\tfrac{1}{2n}\right]$ & $\tfrac{1}{2n}$ & $\left(0,\tfrac{0.5}{2n}\right]$\tabularnewline\addlinespace
\midrule 
\addlinespace
\begin{tabular}{c}
$0<k<2n$\tabularnewline
and $2\nmid k$\tabularnewline
\end{tabular} & $\left[\tfrac{k-1}{2n},\tfrac{k+1}{2n}\right]$ & $\tfrac{1}{n}$ & $\left(\tfrac{k-0.5}{2n},\tfrac{k+0.5}{2n}\right)$\tabularnewline\addlinespace
\midrule 
\addlinespace
\begin{tabular}{c}
$0<k<2n$\tabularnewline
and $2\mid k$\tabularnewline
\end{tabular} & \multirow{1}{*}{$\left[\tfrac{k-1}{2n},\tfrac{k+1}{2n}\right]$} & $\tfrac{1}{n}$ & $\left[\tfrac{k-0.5}{2n},\tfrac{k+0.5}{2n}\right]$\tabularnewline\addlinespace
\midrule 
\addlinespace
$2n$ & $\left[\tfrac{2n-1}{2n},1\right]$ & $\tfrac{1}{2n}$ & $\left[\tfrac{2n-0.5}{2n},1\right)$\tabularnewline\addlinespace
\midrule 
\addlinespace
 & $\necess$ & $0$ & $\necess$\tabularnewline\addlinespace
\bottomrule
\end{tabular}
\end{table}
Since the interior parts are non-overlapping, we can define a function~$\iota_{n}:\left[0,1\right]\rightarrow\mathscr{I}_{n}$
by $\iota_{n}\left(x\right)=[\ell,r]$ if $x\in\textrm{Int}\left([\ell,r]\right)$.
